From Archives to AI: Residential Property Data Across Three Decades in Brunei Darussalam

### 2025-03-25 _tex/manuscript.tex
Built site for gh-pages

\begin{abstract}
This article introduces the first publicly available data set for
analysing the Brunei housing market, covering more than 30,000 property
listings from 1993 to early 2025. The data set, curated from property
advertisements in newspapers and online platforms, includes key
attributes such as price, location, property type, and physical
characteristics, enriched with area-level spatial information.
Comprehensive and historical, it complements the Brunei Darussalam
Central Bank's Residential Property Price Index (RPPI), addressing the
limitations of restricted access to raw RPPI data and its relatively
short timeline since its inception in 2015. Data collection involved
manual transcription from archival sources and automated web scraping
using programmatic methods, supported by innovative processing with
Large Language Models (LLMs) to codify unstructured text. The data set
enables spatial and temporal analysis, with potential applications in
economics, urban planning, and real estate research. Although listing
prices are only a proxy for market values and may deviate from actual
sale prices due to negotiation dynamics and other factors, this data set
still provides a valuable resource for quantitative analyses of housing
market trends and for informing policy decisions.
\end{abstract}

@@

\begin{itemize}
\item
  \textbf{A first-of-its-kind data set for Brunei}. This data set is the
  first publicly available compilation of Brunei's residential property
  data, covering 31,116 listings from 1993 to early 2025. Previous
  studies on Brunei's housing have either relied on recent or
  non-spatial data \citep{ng2022characterising, jamil2025leveraging}, or
  have primarily employed qualitative methods due to the absence of
  structured data \citep{hassan2011cultural, hassan2023sociocultural}.
  Researchers may use this data to explore temporal variations in
  property listings and to compare housing characteristics across
  different regions within Brunei.
\item
  \textbf{Historical and spatial insights}. Spanning over three decades,
  this data set enables analysis of long-term housing trends at various
  administrative levels in Brunei, providing insights into urban
  development patterns, regional differences, and the evolution of
  housing characteristics over time. This historical depth is
  particularly valuable given the lack of data prior to the
  establishment of the Residential Property Price Index (RPPI)
  \citep{bdcb2021technical} in 2015.
\item
  \textbf{Methodological innovation in data curation}. The data
  collection process employs a unique combination of manual
  transcription from archival sources, automated web scraping, and
  AI-based data cleaning using Large Language Models (LLMs). This
  multi-method approach offers a reproducible framework for assembling
  complex data sets, which can be adapted for similar data collection
  efforts in other domains, thereby advancing best practices in the
  field.
\end{itemize}

@@

\textsubscript{Source:
\href{https://Bruneiverse.github.io/house-data/manuscript.qmd.html}{Article
Notebook}}

@@

The data set includes a range of property characteristics suitable for
exploring the relationship between property attributes and prices. This
section clarifies and provides context for the key variables in the data
set.

@@

Property tenure refers to the legal terms under which a person holds
ownership or occupancy rights to a property. In Brunei, property tenure
can be classified into three main categories: Freehold (in perpetuity),
Leasehold, and Strata. The latter two refer to a limited time-limited
ownership, although details about the remaining duration of the tenure
are almost never included in property listings. Strata titles differ
from Leasehold titles in that they grant ownership of a specific portion
of a property, such as an apartment, while sharing ownership of common
areas.

@@

Finally, metadata about the property is included for transparency and
informational purposes. The variable \texttt{agent} specifies the
(anonymised) identifier of the real estate agent or agency responsible
for the listing, while \texttt{source} identifies the platform or medium
from which the listing was obtained, such as a newspaper, magazine, or
website. The \texttt{method} variable details the data collection
approach, which is further elaborated in the section below.

@@

In Brunei Darussalam, the administrative areas are organised
hierarchically into three levels. At the smallest level is the
\emph{kampong}, the Malay word for village. While a typical village
refers to a traditional rural settlement, it is also used to describe an
urbanised area located within or near the capital city or a town. It may
even refer to a part of public housing estates. Several kampongs grouped
together form a \emph{mukim}, which serves as a sub-district
administrative area. Finally, multiple mukims are nested within a
\emph{district}, the largest administrative unit, of which Brunei has
four: Brunei-Muara, Belait, Tutong, and Temburong. In our data set, each
property listing is associated with a specific kampong, mukim, and
district, allowing for spatial analysis at different scales.

Importantly, the names of the kampongs, mukims, and districts have been
harmonised with a standardised naming convention to ensure consistency
across the data set. This also allows for ease of integration into
Geographic Information Systems (GIS) software for spatial analysis and
visualisation, namely the \texttt{\{bruneimap\}} R package
\citep{jamil2024bruneimap}.

@@

The \texttt{date} variable represents the date on which the property
listing was obtained, rather than the date of sale or transaction, and
should be interpreted as a snapshot of market conditions at a given
point in time. For analysis, we recommend aggregating data by quarters,
as represented by the \texttt{quarter} variable. This aggregation helps
address potential issues like missing data (see subsection below) and
provides a more stable and robust representation of market trends,
making it suitable for temporal analysis of the housing market.

@@

Missing values are represented by blank cells in the CSV file, and the
severity of missingness is summarized in Table~\ref{tbl-avail}. In
total, 10.1\% of the records contain missing values for all key house
characteristics (i.e.~plot area, floor area, beds, and baths), which,
depending on the research question, may require imputation or the
exclusion of these records.

@@

Early years data collection was conducted manually, involving the
transcription of property listing details from advertisements into a
digital tabular format. This process was carried out by two of the
authors over a period of nine months, from October 2023 to July 2024,
working at a manageable pace. A total of 12,092 data points were
collected in this manner, which translates to processing approximately
150 entries per week per person. Spreading the task over such an
extended period ensured that transcribers were never under undue time
pressure, which could have led to errors due to fatigue.

The primary sources of the property listings were local newspapers and
magazines. Physical copies were accessed through the National Archive of
Brunei Darussalam, while digital versions, which are digitised replicas
of the physical newspapers, were obtained online. These digital formats
could not be scraped due to their lack of structured data, necessitating
manual transcription.

@@

Data from 2012 up until the present (January 2025) were managed to be
collected using this method, averaging around 1,500 listings per year.
While highly efficient, this process relied heavily on the consistency
of the site structure of the source webpages. Changes to website layouts
or closures over time required significant updates to the scraping
scripts. To overcome these issues, alternative approaches, such as using
Large Language Models (LLMs) were considered. This is explained in the
next subsection.

@@

The primary goal was to extract the house characteristics of interest,
specifically variables 7 to 15 as per Table~\ref{tbl-codebook}, from the
unstructured verbose descriptions scraped from property listing
websites. Each description was processed with a carefully designed
prompt (Figure~\ref{fig-llm-prompt}) to ensure consistent output. This
prompt instructed the model to return only the required information in a
semicolon-separated format, while handling edge cases such as missing
descriptions or non-residential (commercial) properties.

@@

The verbose descriptions were fed into the model one at a time using a
loop, with the LLM extracting and returning the relevant details. Note
that this loop was not parallelised, as the LLM already utilises
multiple cores, and further parallelisation would not yield significant
efficiency gains due to resource constraints. The cleaned results were
then parsed and stored in a data frame, which was then subjected to
manual data-type validation to ensure conformity with the existing data
set (see the last subsection). It takes, on average, 81.7 seconds to
process a single description using a Mac Pro 3.2GHz 16 core Intel Xeon W
with 48GB of DDR4 RAM. We processed 5,055 descriptions from 2020 to 2025
using this method, with a run time of approximately 20 hours in total
(spread over three machines).

@@

Our experiments show that the LLM data extraction process with the
deepseek-r1:14b model achieved an overall accuracy rate of 96.9\% (see
Appendix for complete results). Errors mostly stemmed from incorrect
\texttt{status} classification, likely due to the vagueness of the
advertisement listing. As for the rest of the variables, obvious errors
were flagged and corrected manually during our data validation process
(described in the subsection following the next one). Overall, the LLM
was found to be a valuable tool for extracting structured information
from unstructured text, significantly reducing the time and effort
required for data extraction.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Spelling variations or misspellings, though these were relatively
  straightforward to correct.
\item
  Unknown entries, where the correct kampong could sometimes be inferred
  from the geographical context; otherwise, these were set to
  \texttt{NA}.
\item
  Multiple matches, occurring when two or more kampongs shared the same
  name (e.g., Kampong Panchor in Mukim Mentiri and Kampong Panchor in
  Mukim Lumapas). Additional information from the listing was used to
  determine the correct match, but where this was not possible, these
  entries were also set to \texttt{NA}.
\end{enumerate}

This process was carried out manually using data filtering features in
Microsoft Excel. Once completed, all entries marked as \texttt{NA} were
removed so as to provide complete spatial information for each listing.

@@

To ensure data quality, a series of consistency and validity checks were
performed on the data set, especially after manual transcription and LLM
data cleaning. These checks include

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Outlier detection.} Summary statistics analyses to identify
  and flag anomalous values. For instance, a built-up area recorded as
  0.1 square feet or an implausibly high number of beds and baths (e.g.,
  \textgreater20) would highly likely indicate a possible error,
  prompting manual review. Such anomalies were flagged and manually
  reviewed for correction.
\item
  \textbf{Internal consistency checks.} This made use of substantive
  knowledge about Brunei's housing market
  \citep{jamil2025spatiotemporal}. An example is using the price per
  square foot indicator, whose value typically falls within a known
  range. Therefore any deviations were scrutinised to ensure that
  variables such as price and floor area were correctly recorded. This
  was similarly applied to other variables such as plot area, beds, and
  baths.
\item
  \textbf{Duplicate records detection.} We also performed duplicate
  record detection to identify any repeated entries that might have
  arisen from overlapping data sources or transcription errors. Any
  duplicates that were identified were carefully reviewed and removed to
  ensure that each property listing was uniquely represented in the span
  of one calendar month.
\end{enumerate}

@@

\section{Limitations}\label{limitations}

Listing prices in our data set serve as a proxy for market values,
capturing advertised trends rather than final sale outcomes. This
enables timely analysis of market sentiment, even though factors such as
negotiation dynamics, seller strategies, and market conditions may cause
deviations from actual transaction prices.

Despite significant efforts to ensure data quality, some limitations
remain. First, integrating historical data from manually transcribed
sources with later web-scraped data may introduce inconsistencies
affecting comparability over time. Second, although duplicate listings
were carefully reviewed and removed, there remains a slight possibility
of residual duplicates in the data set. Thirdly, while we have
confidence in the data quality from 2015 to 2024, property price trends
between 1993 and 2014 cannot be fully verified. Nonetheless, this study
serves as a valuable starting point. Future research could benefit
greatly from access to administrative transaction data, which would
allow for more comprehensive and accurate analyses.

Finally, while significant effort was made to harmonise spatial data,
the matching of kampong names to standardised references may not be
entirely error-free. However, aggregation to the mukim level provides a
reliable alternative for spatial analyses, ensuring that the data set
remains valuable for research and analysis.

\section{Ethics}\label{ethics}

@@

The data collected consisted exclusively of non-copyrightable factual
information, such as property characteristics and spatial locations, and
excluded any potentially copyrighted content such as images. To ensure
privacy, no personally identifiable information, including specific
property addresses, was scraped nor included in the data set. To this
end, data from the description fields processed by the LLM are not
included in the data set, as they may contain sensitive information such
as contact details and names of companies. Furthermore, we have
anonymised the names of the real estate agents and companies in the data
set.

\section{CRediT Author Statement}\label{credit-author-statement}

@@

\section{Acknowledgements}\label{acknowledgements}

The authors gratefully acknowledge the contributions of Atikah Farhain
Yahya, Nurulhanisah Abdul Manan, and Nina Zuhairi towards the collection
and processing of the data contained within. We also thank the Brunei
Darussalam Central Bank (BDCB) for the engaging discussions and support,
which were instrumental in the initiation of this project.

\section{Declaration of Competing
Interests}\label{declaration-of-competing-interests}

@@

\section{Appendix}\label{appendix}

@@

@@

\subsection{Comparison to RPPI Data}\label{comparison-to-rppi-data}

@@

\subsection{LLM Accuracy Test}\label{sec-apx-llm}

@@

OpenAI's models topped the accuracy charts, with the o1-mini and gpt-4o
models achieving the accuracy scores of 99.2\% and 98.9\% respectively.
The reasoning model deepseek-r1:14b was the best performing locally run
model, scoring 96.9\% accuracy. Evidently, the smaller the model, the
less accurate the extraction process (cf.~llama3.2 70.8\%). Most
inaccuracies occurred in the \texttt{status} variable, where models
struggled to parse the correct build status from vague advertisement
descriptions. However, key variables such as \texttt{price},
\texttt{type}, \texttt{plot\_area}, \texttt{floor\_area}, \texttt{beds},
and \texttt{baths} are generally reliable (\textgreater90\% accuracy).

>>>>

\begin{abstract}
This article introduces the first publicly available data set for
analysing the Brunei housing market, covering more than 30,000 property
listings from 1993 to early 2025. The data set, curated from property
advertisements in newspapers and online platforms, includes key
attributes such as price, location, property type, and physical
characteristics, enriched with area-level spatial information.
Comprehensive and historical, it complements the Brunei Darussalam
Central Bank's Residential Property Price Index (RPPI), addressing the
limitations of restricted access to raw RPPI data and its relatively
short timeline since its inception in 2015. Data collection involved
manual transcription from archival sources and automated web scraping
using programmatic techniques, supported by innovative processing with
Large Language Models (LLMs) to codify unstructured text. The data set
enables spatial and temporal analysis, with potential applications in
economics, urban planning, and real estate research. Although listing
prices are only a proxy for market values and may deviate from actual
sale prices due to negotiation dynamics and other factors, this data set
still provides a valuable resource for quantitative analyses of housing
market trends and for informing policy decisions.
\end{abstract}

@@

\begin{itemize}
\item
  \textbf{A first-of-its-kind data set for Brunei}. This data set is the
  first publicly available compilation of Brunei's residential property
  data, covering 31,116 listings from 1993 to early 2025. Previous
  studies on Brunei's housing have either relied on recent or
  non-spatial data \citep{ng2022characterising, jamil2025leveraging}, or
  have primarily employed qualitative methods due to the absence of
  structured data \citep{hassan2011cultural, hassan2023sociocultural}.
  Researchers may use this data to explore temporal variations in
  property listings and to compare housing characteristics across
  different regions within Brunei.
\item
  \textbf{Historical and spatial insights}. Spanning over three decades,
  this data set enables analysis of long-term housing trends at various
  administrative levels in Brunei, providing insights into urban
  development patterns, regional differences, and the evolution of
  housing characteristics over time. This historical depth is
  particularly valuable given the lack of data prior to the
  establishment of the Residential Property Price Index (RPPI)
  \citep{bdcb2021technical} in 2015.
\item
  \textbf{Methodological innovation in data curation}. The data
  collection process employs a unique combination of manual
  transcription from archival sources, automated web scraping, and
  AI-based data cleaning using Large Language Models (LLMs). This
  multimethod approach offers a reproducible framework for assembling
  complex data sets, which can be adapted for similar data collection
  efforts in other domains, thereby advancing best practices within the
  field.
\end{itemize}

@@

\textsubscript{Source:
\href{https://Bruneiverse.github.io/house-data/manuscript-preview.html}{Article
Notebook}}

@@

The data set includes a range of property characteristics suitable for
exploring the relationship between property attributes and prices. This
section clarifies and provides context for the key variables in the data
set. A summary of the property characteristics is presented in
Table~\ref{tbl-summary}.

@@

Property tenure refers to the legal terms under which a person holds
ownership or occupancy rights to a property. In Brunei, property tenure
can be classified into three main categories: Freehold (in perpetuity),
Leasehold, and Strata. The latter two refer to a time-limited ownership,
although details about the remaining duration of the tenure are almost
never included in property listings. Strata titles differ from Leasehold
titles in that they grant ownership of a specific portion of a property,
such as an apartment, while sharing ownership of common areas.

@@

Finally, metadata regarding each property are also included. The
variable \texttt{agent} specifies the (anonymised) identifier of the
real estate agent or agency responsible for the listing, while
\texttt{source} identifies the platform or medium from which the listing
was obtained, such as a newspaper, magazine, or website. The
\texttt{method} variable details the data collection approach, which is
further elaborated in the section below.

@@

In Brunei Darussalam, the administrative areas are organised
hierarchically into three levels. At the smallest level is the
\emph{kampong}, the Malay word for village. While a typical village
refers to a traditional rural settlement, it is also used to describe an
urbanised area located within or near the capital city or a town. It may
even refer to a part of public housing estates. Several kampongs grouped
together form a \emph{mukim}, which serves as a sub-district
administrative area (see Figure~\ref{fig-spatial}). Finally, multiple
mukims are nested within a \emph{district}, the largest administrative
unit, of which Brunei has four: Brunei-Muara, Belait, Tutong, and
Temburong. In our data set, each property listing is associated with a
distinct kampong, mukim, and district, allowing for spatial analysis at
different scales.

Importantly, the names of the kampongs, mukims, and districts have been
harmonised with a standardised naming convention to ensure consistency
across the data set. This also allows for ease of integration with
Geographic Information Systems (GIS) software for spatial analysis and
visualisation, namely the \texttt{\{bruneimap\}} R package
\citep{jamil2024bruneimap}.

@@

The \texttt{date} variable represents the date on which the property
listing was obtained, rather than the date of sale or transaction, and
should be interpreted as a snapshot of market conditions at a specific
point in time. Figure~\ref{fig-price-evolution} illustrates the price
evolution over time. For analysis, we recommend aggregating data by
quarters, as represented by the \texttt{quarter} variable. This
aggregation helps address potential issues like missing data (see
subsection below) and provides a more stable and robust representation
of market trends, making it suitable for temporal analysis of the
housing market.

@@

Missing values are represented by blank cells in the CSV file. The
severity of missingness is summarised in Table~\ref{tbl-avail} and
patterns visualised in Figure~\ref{fig-missing-pattern}. In total,
10.1\% of the records contain missing values for all key house
characteristics (i.e.~plot area, floor area, beds, and baths), which,
depending on the research question, may require imputation or the
exclusion of these records.

@@

Early years data collection was conducted manually, involving the
transcription of property listing details from advertisements into a
digital tabular format. This process was carried out by two of the
authors over a period of nine months, from October 2023 to July 2024,
working at a manageable pace. A total of 12,092 data points were
collected in this manner, which translates to processing approximately
150 entries per week per person. Spreading the task over such an
extended period ensured that transcribers were never under time
pressure, which could have led to errors due to fatigue.

The primary sources of the property listings were local newspapers and
magazines. Physical copies were accessed through the National Archive of
Brunei Darussalam, while digital versions, which are digitised replicas
of the physical newspapers, were obtained online. These digital formats
were not structured in a way that allowed for automated scraping, hence
the need for manual transcription.

@@

Data from 2012 up until the present (February 2025) were managed to be
collected using this method, averaging around 1,500 listings per year.
While highly efficient, this process relied heavily on the consistency
of the site structure of the source webpages. Changes to website layouts
or closures over time required significant updates to the scraping
scripts. To overcome these issues, alternative approaches, such as using
Large Language Models (LLMs), were considered. This is explained in the
next subsection.

@@

The primary goal was to extract the house characteristics of interest,
specifically variables 7 to 15 as per Table~\ref{tbl-codebook}, from the
unstructured verbose descriptions scraped from property listing
websites. Each description was processed with a carefully crafted prompt
(Figure~\ref{fig-llm-prompt}) to ensure consistent output. This prompt
instructed the model to return only the required information in a
semicolon-separated format, while handling edge cases such as missing
descriptions or non-residential (commercial) properties.

@@

The verbose descriptions were fed into the model one at a time using a
loop, with the LLM extracting and returning the relevant details. Note
that this loop was not parallelised, as the LLM already utilises
multiple cores, and further parallelisation would not yield significant
efficiency gains due to resource constraints. The cleaned results were
then parsed and stored in a data frame, which was then subjected to
manual data-type validation to ensure conformity with the existing data
set (see the last subsection). It takes, on average, 81.7 seconds to
process a single description using a Mac Pro 3.2GHz 16 core Intel Xeon W
with 48GB of DDR4 RAM. We processed 5,055 descriptions from 2020 to 2025
using this method, with a run time of approximately 20 hours in total
spread over three machines.

@@

Our experiments show that the LLM data extraction process with the
deepseek-r1:14b model achieved an overall accuracy rate of 96.9\% (see
Appendix for complete results). Errors mostly stemmed from incorrect
\texttt{status} classification, likely due to the vagueness of the
advertisement listing. As for the rest of the variables, clear errors
were flagged and corrected manually during our data validation process
(described in the subsection following the next one). Overall, the LLM
was found to be a valuable tool for extracting structured information
from unstructured text, significantly reducing the time and effort
required for data extraction.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Spelling variations and misspellings, though these were relatively
  straightforward to correct.
\item
  Unknown entries, where the correct kampong could sometimes be inferred
  from the geographical context; otherwise, these were set to
  \texttt{NA}.
\item
  Multiple matches, occurring when two or more kampongs shared the same
  name (e.g., Kampong Panchor in Mukim Mentiri and Kampong Panchor in
  Mukim Lumapas). Additional information from the listing was used to
  determine the correct match, but where this was not possible, these
  entries were also set to \texttt{NA}.
\end{enumerate}

This process was carried out manually using data filtering features in
Microsoft Excel. Once completed, all entries marked as \texttt{NA} were
removed so as to provide complete spatial coverage for the data set.

@@

To ensure data quality, a series of consistency and validity checks were
performed on the data set, especially after manual transcription and LLM
data cleaning. These checks include:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textbf{Outlier detection.} Statistical summaries were analysed to
  identify and flag anomalous values. For instance, a built-up area
  recorded as 0.1 square feet or an implausibly high number of beds and
  baths (e.g., \textgreater20) would likely indicate an error, prompting
  review. Such anomalies were flagged and manually reviewed for
  correction.
\item
  \textbf{Internal consistency checks.} This made use of substantive
  knowledge about Brunei's housing market
  \citep{jamil2025spatiotemporal}. An example is using the price per
  square foot indicator, whose value typically falls within a known
  range. Therefore any deviations were scrutinised to ensure that
  variables such as price and floor area were correctly recorded. This
  was similarly applied to other variables such as plot area, beds, and
  baths.
\item
  \textbf{Duplicate records detection.} We also performed duplicate
  record detection to identify any repeated entries that might have
  arisen from overlapping data sources or transcription errors. Any
  duplicates that were identified were carefully reviewed and removed to
  ensure that each property listing was uniquely represented in the span
  of one calendar month.
\end{enumerate}

@@

\section*{Limitations}\label{limitations}
\addcontentsline{toc}{section}{Limitations}

Listing prices in our data set serve as a proxy for market values,
capturing advertised trends rather than final sale outcomes. While this
allows for timely analysis of market sentiment, actual transaction
prices may differ due to negotiation dynamics, seller strategies, and
broader market conditions.

Despite significant efforts to ensure data quality, some limitations
remain. First, integrating historical data from manually transcribed
sources with later web-scraped data may introduce inconsistencies,
potentially affecting comparability over time. Second, although
duplicate listings were carefully reviewed and removed, there remains a
slight possibility of residual duplicates within the data set. Thirdly,
while we have confidence in the data quality from 2015 to 2024, property
price trends between 1993 and 2014 cannot be fully verified.
Nonetheless, this study serves as a valuable starting point. Future
research could benefit greatly from access to administrative transaction
data, which would allow for more comprehensive and accurate analyses.

Finally, while significant effort was made to harmonise spatial data,
matching kampong names to standardised references may not be entirely
error-free. However, aggregation to the mukim level provides a reliable
alternative for spatial analyses, ensuring that the data set remains
valuable for research and analysis.

\section*{Ethics}\label{ethics}
\addcontentsline{toc}{section}{Ethics}

@@

The data collected consisted exclusively of non-copyrightable factual
information, such as property characteristics and spatial locations, and
excluded any potentially copyrighted content such as images. To ensure
privacy, no personally identifiable information, including specific
property addresses, was scraped nor included in the data set. To this
end, data from the description fields processed by the LLM are not
included in the data set, as they may contain sensitive information such
as contact details and company names. The names of real estate agents
and companies have been anonymised to ensure privacy.

\section*{CRediT Author Statement}\label{credit-author-statement}
\addcontentsline{toc}{section}{CRediT Author Statement}

@@

\section*{Acknowledgements}\label{acknowledgements}
\addcontentsline{toc}{section}{Acknowledgements}

The authors gratefully acknowledge the contributions of Atikah Farhain
Yahya, Nurulhanisah Abdul Manan, and Nina Zuhairi for their assistance
in collecting and processing the data presented in this study. The
authors also extend their thanks to the Brunei Darussalam Central Bank
(BDCB) for engaging discussions and valuable support, which were
instrumental in initiating this project.

\section*{Declaration of Competing
Interests}\label{declaration-of-competing-interests}
\addcontentsline{toc}{section}{Declaration of Competing Interests}

@@

\section*{Appendix}\label{appendix}
\addcontentsline{toc}{section}{Appendix}

@@

Figure~\ref{fig-corr} shows the pairwise correlation plot of the numeric
variables in the data set.

@@

\subsection*{Comparison to RPPI Data}\label{comparison-to-rppi-data}
\addcontentsline{toc}{subsection}{Comparison to RPPI Data}

@@

\subsection*{LLM Accuracy Test}\label{llm-accuracy-test}
\addcontentsline{toc}{subsection}{LLM Accuracy Test}

@@

Figure~\ref{fig-llmtest} and Table~\ref{tbl-llmtest-time} show the
accuracy results for each model. OpenAI's models topped the accuracy
charts, with the o1-mini and gpt-4o models achieving the accuracy scores
of 99.2\% and 98.9\% respectively. The reasoning model deepseek-r1:14b
was the best performing locally run model, scoring 96.9\% accuracy.
Evidently, the smaller the model, the less accurate the extraction
process (cf.~llama3.2 70.8\%). Most inaccuracies occurred in the
\texttt{status} variable, where models struggled to parse the correct
build status from vague advertisement descriptions. However, key
variables such as \texttt{price}, \texttt{type}, \texttt{plot\_area},
\texttt{floor\_area}, \texttt{beds}, and \texttt{baths} are generally
reliable (\textgreater90\% accuracy).
